---
title: "W203-Lab3_Project"
output: pdf_document
---

```{r}
setwd("/Users/klomurray/Desktop/Course Materials/Statistics/Lab3")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
crime<-read.csv("crime_v2.csv", stringsAsFactors = FALSE)

```




```{r}
nrow(crime)
tail(crime)
```

There are 6 rows of data that are completely null. These rows will be omitted. 

```{r}
crime<-na.omit(crime)
nrow(crime)
```

```{r}
summary(crime)
```


```{r}
length(unique(crime$county))
```

There is a duplicate value for county 193. All values for that county are the same. The duplicate version of 193 should be excluded. 
```{r}
print(crime[duplicated(crime$county),"county"])

print(subset(crime, county==193))
```

```{r}

crime <- crime[!duplicated(crime),]
nrow(crime)

```

According to the internet, NC has 100 counties so some counties appear to be missing. Question: Is there any pattern to the missing counties such as regions missing?

```{r}
library(reshape2)
library(ggplot2)
meltData<-melt(crime)

p <- ggplot(meltData, aes(factor(variable), value)) 
p + geom_boxplot() + facet_wrap(~variable, scale="free")


```

Reviewing the boxplot some variables have outliers that should be investigated. These include urban, west, and wser. 



